Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-17 snapshot_system/failover.tex
modify analysis

We  compare the impact of losing $d$ machines 
to the the VC and VO approaches.  
The replication degree of the backup storage 
is $r$ for regular content blocks and $r=3$ is a typical setting in the distributed
file system~\cite{Hadoop,GFS}.
in The VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
Noted that the storage cost for VO with full deduplication is $b_u *r$
while it is
\[ r*b*s(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
\]

When $d<r$, there is no loss of data in the snapshot storage.
When $d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
suffer the loss of their snapshots.
We use the following parameters  during the analysis
\begin{itemize}
\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the bakcup storage.
$d$ is the number of machines failed.
\item In the VC approach, $s_c$  of them in the backup storage
are shared by others with a zipf distribution. $(1-s_c)$ 
of them  is unique (nobody shares with them).
$L_c$ is the average number of VMs sharing a block (if it is in CDS for the VC approach.
$b_c$ is the number of shared blocks in VC.
\item In the VO approach, $s_o$ is the number of blocks shared.
$L_o$ is the average number of VMs sharing a block. 
\item $b$ is the  number of blocks stored in the storage after deduplication.
 \end{itemize}

@@

\comments{
\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}
}

@@

\comments{
Prob(i-th block shared by (V-i+1) machines = X/i.
b
Sum (X/i) =1.      Thus       X= 1/ ln (V).
Length of sharing=  Probality(this block is shared with 1 VM) 1 + Probablity(this block shared by 2 VM) 2+..] =  X *V +X*(V-1)/2+ X*(V-2)/3 +..
=  X * sum (V-i+1)/I   for I from 1 to V.
=  (V+1) sum (X/i) . Sum(X) =  (V+1) -  X*V= V(1- 1/lnV) +1.
}

@@

%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
%if we wanted to include it we probably want a model that includes containers, but that might be too complex
%to be useful.

\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]

>>>>

We  compare the impact of losing $d$ machines 
to the the VC and VO approaches.  
The replication degree of the backup storage 
is $r$ for regular content blocks and $r=3$ is a typical setting in the distributed
file system~\cite{Hadoop,GFS}.
in The VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
Noted that the storage cost for VO with full deduplication is $b_u *r$
while it is
\[ r*b*\delta(1 -   (\frac{k}{b_u})^{1-\alpha}) +k*(r-r_c).
\]

For each rank $i$ block which appears $C_i$ times  among $V$ virtual machines.
Assigning this block to virtual machines can be viewed as a classical ball-bin assignment
approximated by a Poisson distribution. Namely the virtual machines that share this block
is approximated as $1 -  e^{C_i/V}$.
Thus the average number of VMs that share a block is:
\[
(1-\delta) + \delta \sum_1^{u_b} \frac{1 -  e^{C_i/V}}{u_b}.
\]
Any failure of a block would impact the above number of virtual machines.
In VO, the number of VMs that share a block is:
\[
\sum_1^{u_b'} \frac{1 -  e^{C_i'/V}}{u_b'}.
\]

Next we discuss how a failure of $d$ machines impacts the VM snapshots in VC.
When $d<r$, there is no loss of data in the snapshot storage.
When $r_c> d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
suffer the loss of their snapshots.
When $d \ge r_c$, some of CDS blocks are affected.
In VC, the blocks in CDS are stored in a container manner (superblock), and they are shared by many VMs.
The number of data containers stored with replication degree $r$ for
referenced by each VM is:
\[
N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha})
\]
The number of CDS data containers stored with replication degree $r_c$ for
referenced by each VM is:
\[
N_2= \frac{b}{v*s}\delta (\frac{k}{b_u})^{1-\alpha}.
\]

When there are $r \le d<r_c$ machines failed and the probability of
a container failure depends on if all replicas of this container reside in the failed machines.
\begin{multline}
Probability (\mbox{ a VM fails in VC})\\
= 1- Probability (\mbox{ a VM has no data container loss}) \\
= 1-  Probability(\mbox{ A container has no data loss})^{N_1}
%\end{split}
\end{multline}

%Probablity(\mbox { no loss for this  block}) = 1 - Probability (\mbox{ this block in d failed machiens})
\begin{multline}
%\begin{split}
Probability(\mbox{A container no data loss})\\
= 1- Probability (\mbox{ this container is in d failed machines})\\
=  1- \frac{\binom{d}{r}} { \binom{p}{r} }.
%\end{split}
\end{multline}

When $r_c \leq d$, the CDS data containers in VC can also have a loss. 
\begin{multline}
Probability (\mbox{ a VM fails in VC})\\
= 1-  Probability(\mbox{ A container has no data loss})^{N_1}* \\
Probability(\mbox{ A CDS container has no data loss})^{N_2}\\
= 1 - 
(\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2} 
%\end{split}
\end{multline}

By comparison, the probability that a VM has data loss is close to
1 once  there are  $d \ge r$ failed machines. That is because there are more data blocks
shared among VMs. Any failure of these blocks causes many more VMs to fail.

\comments{
We use the following parameters  during the analysis
\begin{itemize}
\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the backup storage.
$d$ is the number of machines failed.
\item In the VC approach, $s_c$  of them in the backup storage
are shared by others with a zipf distribution. $(1-s_c)$ 
of them  is unique (nobody shares with them).
$L_c$ is the average number of VMs sharing a block (if it is in CDS for the VC approach.
$b_c$ is the number of shared blocks in VC.
\item In the VO approach, $s_o$ is the number of blocks shared.
$L_o$ is the average number of VMs sharing a block. 
\item $b$ is the  number of blocks stored in the storage after deduplication.
 \end{itemize}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}

@@

@@

%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
%if we wanted to include it we probably want a model that includes containers, but that might be too complex
%to be useful.
}
\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]
